The Impact of Educational Expenses of New Coders

### 2021-04-21 outputs/paper/paper.Rmd
Edit model validation table
Edit model evaluation tables

```{r, include=FALSE}
# Source: https://stefaneng.github.io/apa_correlation_table/
# install.packages("Hmisc")
library(Hmisc)

@@

# summary(multiReg3)
stargazer::stargazer(multiReg1, multiReg2, multiReg3, 
          title = "Predictions of money for learning across experimental conditions", 
          header = FALSE,
          type = "latex")
```

@@

## Model validation with RMSE

@@

RSQ <- function(model) {
  return(summary(model)$r.squared)
}

MSE <- function(error) {
  return(mean(error^2))
}

RMSE <- function(error) {
  return(sqrt(mean(error^2))) 
}

vecModel <-
  c("Model (1)", "Model (2)", "Model (3)")

@@

dfModelValid <-
  data.frame(vecModel, vecRSQ, vecMSE, vecRMSE) %>%
  kable(caption = "Model validation",
        booktabs = TRUE,
        col.names = c("Model", "R-squared", "MSE", "RMSE")) %>%
  column_spec(column = 1, width = "4cm") %>%
  column_spec(column = 2:4, width = "3cm")

@@

# If R-squared is closer to 0 = Good!
# Model3 has the lowest RMSE among the 3 models => Model3 is the best!

>>>>

```{r, include=FALSE}
#### Custom functions ####

### Format number
# Source: https://stackoverflow.com/questions/29465941/format-number-in-r-with-both-comma-thousands-separator-and-specified-decimals

formatNumber <- function(numb, decimal) {
  return(format(round(as.numeric(numb), decimal), nsmall=decimal, big.mark=",")) 
}

### APA style correlation matrix 
# Source: https://stefaneng.github.io/apa_correlation_table/
# install.packages("Hmisc")
library(Hmisc)

@@

# summary(multiReg3)
stargazer::stargazer(multiReg1, multiReg2, multiReg3, 
          title = "Predictions of money for learning", 
          header = FALSE,
          type = "latex")
```

@@

## Model Validation

Discuss model validation here...

@@

### Define functions for R-squared, MSE, and RMSE
RSQ <- function(model) {
  result <- summary(model)$r.squared
  return(formatNumber(result, 3))
}

MSE <- function(error) {
  result <- mean(error^2)
  return(formatNumber(result, 3))  
}

RMSE <- function(error) {
  result <- sqrt(mean(error^2))
  return(formatNumber(result, 3)) 
}

```{r, echo=FALSE, warning=FALSE, message=FALSE}

### Calculate R-squared, MSE, and RMSE for each model 
vecModel <-
  c("Model (1)", "Model (2)", "Model (3)")

@@

### Display the result in a table
dfModelValid <-
  data.frame(vecModel, vecRSQ, vecMSE, vecRMSE) %>%
  kable(caption = "Results of model validation metrics",
        booktabs = TRUE,
        col.names = c("Model", "R-squared", "MSE", "RMSE")) %>%
  column_spec(column = 1, width = "4cm") %>%
  column_spec(column = 2:4, width = "3cm")

@@

# If R-squared is closer to 0 = Good!
# Model3 has the lowest RMSE among the 3 models => Model3 is the best!
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}

### Calculate R-squared, MSE, and RMSE for each model
vecModel_city <-
  c("Model (1)", "Model (2)", "Model (3)", "Model (4)")

vecRSQ_city <- 
  c(RSQ(linReg1), RSQ(linReg2), RSQ(linReg3), RSQ(linReg4))

vecMSE_city <-
  c(MSE(linReg1$residuals), MSE(linReg2$residuals), MSE(linReg3$residuals),  MSE(linReg4$residuals))

vecRMSE_city <-
  c(RMSE(linReg1$residuals), RMSE(linReg2$residuals), RMSE(linReg3$residuals), RMSE(linReg4$residuals))

### Display the result in a table
dfModelValidCity <-
  data.frame(vecModel_city, vecRSQ_city, vecMSE_city, vecRMSE_city) %>%
  kable(caption = "Results of model validation metrics",
        booktabs = TRUE,
        col.names = c("Model", "R-squared", "MSE", "RMSE")) %>%
  column_spec(column = 1, width = "4cm") %>%
  column_spec(column = 2:4, width = "3cm")

dfModelValidCity
